Supplementary Material (SM)

### 2020-04-28 Current Version/SM.Rmd
reorganize

---
title: "Supplementary Material (SM)"
bibliography: ref.bib
output:
  pdf_document: 
    extra_dependencies:
      - float
      - flafter
    fig_caption: yes
    fig_height: 3
    fig_width: 4
    keep_tex: yes
    number_sections: yes
header-includes:
  - \usepackage{xr}
  - \usepackage{mathtools}
  - \usepackage{mathrsfs}
  - \usepackage{hyperref}
  - \usepackage[left]{lineno}
  - \usepackage{amsmath}
  - \linenumbers
  - \externaldocument{draft}  
editor_options: 
  chunk_output_type: console
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = "H", out.extra = "")
```

@@

```{r, echo=F, fig.align='center', out.width='100%', fig.cap='\\label{num_corr} Numerical estimate for the correlations of selection gradients and competition coefficients.'}
knitr::include_graphics('/home/bb/Gits/branching.brownian.motion.and.spde/.A White Noise Approach To Evolutionary Ecology/corrs.png')
```

>>>>

---
title: "Supplementary Material (SM)"
bibliography: ref.bib
output:
  pdf_document: 
    extra_dependencies:
      - float
      - flafter
    fig_caption: yes
    fig_height: 3
    fig_width: 4
    keep_tex: yes
    number_sections: yes
header-includes:
  - \usepackage{xr}
  - \usepackage{mathtools}
  - \usepackage{mathrsfs}
  - \usepackage{hyperref}
  - \usepackage[left]{lineno}
  - \usepackage{amsmath}
  - \linenumbers
  - \externaldocument{Current-Version}  
editor_options: 
  chunk_output_type: console
---

```{r global_options, include=FALSE}
options(tinytex.clean = FALSE)
knitr::opts_chunk$set(fig.pos = "H", out.extra = "")
```

@@

```{r, echo=F, fig.align='center', out.width='100%', fig.cap='\\label{num_corr} Numerical estimate for the correlations of selection gradients and competition coefficients.'}
knitr::include_graphics('/home/bb/Gits/branching.brownian.motion.and.spde/Current Version/corrs.png')
```

\newpage
